Bird beak's elaboration and exploration

### 2022-10-17 Analysis/11-variance_partitioning.Rmd
Update 11-variance_partitioning.Rmd

>>>>

This script explores the meaning of the variance explained in big multidimensional MCMCglmm with variable sample sizes.

# Variance explained in a simple model

# More complex model with equal sample size

# Model with different sample sizes

# Model used in this paper (8D + 32 terms)

Here the model is highly dimensional and the terms sample sizes vary by two orders of magnitude.
